Holomorphic field theories and higher algebra

### 2024-08-19 draft.tex
fix epigraph

\usepackage{macros, setspace}

@@

\dedicatory{To Yuri Manin, with gratitude and admiration.}

\maketitle
\tableofcontents

@@

A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
When we do this, we can split it up into its chiral and anti-chiral `sectors'.
By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
The holomorphic part is described by the following action
\beqn
\int_\Sigma \beta \wedge \dbar \gamma
\eeqn
where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
There is also a coupling between the chiral and anti-chiral sectors, 
for more details we refer to \cite{Kapustin,GGW}. 
This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta-\gamma$-\textit{system}.
It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.

There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta-\gamma$ system'.
The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
Above we took this bundle to be trivial.
The fields of the theory consist of pairs 
\begin{align*}
\gamma & \in \Gamma(X,V)\\
\beta & \in \Omega^{n,n-1}(X,V^*) .
\end{align*}
The action functional is identical $\int_X \beta \wedge \dbar \gamma$.

Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
\beqn
\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
\eeqn
For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
This is one of the key differences between the ordinary $\beta-\gamma$ system and its higher dimensional version.
Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
\beqn
\dbar \mu + \frac12 [\mu,\mu] = 0 ,
\eeqn
where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
\subsection{Local version and examples from supersymmetric field theories}

@@

There is the following local characterization of a holomorphic field theory which allows us to connect directly to supersymmetric field theories. 
Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, meaning that there is an action buy the $2n$-dimensional Lie algebra spanned by the vector fields $\del / \del {z_i}, \del / \del {\zbar_i}$ for $i=1,\ldots,n$. 
In a holomorphic theory we require that the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act homotopically trivial. 
In the derived world this is prescribed by the data of homotopy trivializations for such vector fields.

@@

@@

Let $V$ be a vector space.
Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta-\gamma$ system with values in~$V$.
To a disc $D = D_r(z)$ this assigns the following cochain complex
\beqn
\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
\eeqn
where the differential is $\dbar + \triangle$ which we will explain momentarily. 
We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
\beqn
\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
\eeqn
The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
The vertex algebra associated to this disk algebra is the familiar $\beta-\gamma$-vertex algebra.

@@

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}

\owen{We should also discuss how these can reduce to LG B-models, as precursor to the Hori-Tong dualities.}

A sheaf of chiral differential operators is a `chiralization' the familiar sheaf of differential operators on a complex manifold \cite{}.
It is a sheaf of vertex algebras $\CDO_X$ on a complex manifold $X$ which satisfies the property that under the Zhu construction one has an isomorphism of sheaves of associative algebras
\beqn
\text{Zhu}(\CDO_X) \simeq \cD_X
\eeqn
where $\cD_X$ is the sheaf of differential operators.

Unlike the sheaf of differential operators, one needs to fix additional data in order to define a sheaf of chiral differential operators. 
For a smooth complex manifold $X$, one of the main results of \cite{} is that the obstruction to the existence of such a sheaf is given by
\beqn
\ch_2(\T_X) \in H^{2}(X, \Omega^{2,cl}_X) 
\eeqn
and the space of all such algebras of chiral differential operators is a torsor for the group $H^{1}(X, \Omega^{2,cl}_X)$.
Here $\Omega^{2,cl}_X$ is the sheaf of closed holomorphic two-forms on $X$.

Locally, on an affine patch in $X$, the vertex algebra $\CDO_X$ is equivalent to $N$-copies of the familiar $\beta\gamma$ vertex algebra, where $N = \dim_\CC(X)$. 
We have seen that there is a natural generalization of the $\beta\gamma$ system to a holomorphic factorization algebra in any dimension.

\begin{dfn}\label{dfn:cdo}
A {\em sheaf of $n$-CDOs} on a manifold $X$ (of complex dimension $N$) is a sheaf of $n$-dimensional holomorphically translation invariant factorization algebras whose restriction to any $n$-disc is equivalent to the $n$-dimensional $\beta\gamma$ system (with target $\CC^N$). 
\end{dfn}

\begin{thm}\label{thm:cdo}
Suppose $X$ is a complex manifold satisfying 
\[
{\rm ch}_{n+1} (\T_X) = 0 \in H^{n+1} \big(X , \Omega^{n+1,cl}_X\big).
\]
Then, the set of equivalence classes of higher dimensional CDO's on $X$ is a torsor for the group $H^n \big(X , \Omega^{n+1, cl}_X\big)$. 
If ${\rm ch}_{n+1}(\T_X) \ne 0$ then there does not exist a sheaf of higher CDO's on $X$. 
\end{thm}

Anticipated by Witten, and proved in \cite{GGW}, the sheaf of chiral differential operators is given by the algebra of local operators of a familiar chiral CFT: the $\beta\gamma$ system of maps $\CC \to X$.
In this note, we have described a higher dimensional analog of this system as a holomorphic $\sigma$-model of maps $\CC^n \to X$. 
We have already met the higher dimensional $\beta\gamma$ system on $\CC^n$.
This is an $n$-dimensional holomorphic system described by an $n$-dimensional translation invariant factorization algebra.
In part, the fields of this system constituted a holomorphic map $\gamma \colon \CC^n \to \CC^N$ together with its conjugate field $\beta$. ''

We can reformulate this theorem to stress the role of the higher dimensional holomorphic OPE. 
An alternative to Definition \ref{dfn:cdo} would be to first take the cohomology of the state space of the $\beta\gamma$ system to obtain the structure of a holomorphic $\PP_n$ algebra.
Then, one can define a sheaf of higher CDO's as a sheaf of holomorphic $\PP_n$ algebras which is locally of the form \eqref{eqn:bgope}. 
Theorem \ref{thm:cdo} still applies to show that a necessary condition for such a sheaf to exist is the vanishing of the $(n+1)$ component of the Chern character of $X$. 
The global sections of such a sheaf will give rise to a single holomorphic $\PP_n$ algebra.

Let's unravel this approach in the case $n=2$. 
Label the local coordinate on the target by $\{w^i\}_{i=1,\ldots,N}$.

The cohomology of the state space of the $2$-dimensional $\beta\gamma$ system is a graded polynomial algebra of the form
%\[
%\CC\big[\partial_{z_i}^{\bu \geq 0} \gamma, \partial^{\bu\geq 0}_{z_i} \beta \big]
%\]
\[
\CC\bigg[\gamma^i[k,\ell] \; , \; \beta_j [k,\ell] \bigg]_{k,\ell \geq 0} .
\]
For $k,\ell \geq 0$ and $i,j=1,\ldots N$ the generator $\gamma^i[k,\ell]$ is of cohomological degree zero and the generator $\beta_j[k,\ell]$ is of cohomological degree $1$.

The higher OPEs $\{\gamma^i[k,\ell], \gamma^j [p,q]\}^{r,s} = 0$, $\{\beta^i[k,\ell], \beta^j [p,q]\}^{r,s} = 0$ all vanish. 
There is a nontrivial higher OPE between $\gamma^i$ and $\beta_j$, the simplest of such reads
\[
\big\{\gamma^i[0,0] , \beta_j[-1,-1] \big\}[r,s] = \delta_{r,0} \delta_{s,0} .
\]
In general, 
\beqn\label{eqn:bgope}
\big\{\gamma^i[k,\ell] , \beta_j[p-1,q-1] \big\}[r,s] = \delta_{r,k+p} \delta_{s,\ell+q} .
\eeqn

\subsubsection{Global sections, an example}

We give a concrete description of 2-CDO's on the manifold $X = \PP^1$.
In this case there is a unique sheaf of 2-CDO's that we denote by $2\CDO_{\PP^1}$ (here we are using the holomorphic $\PP_2$ description as the cohomology of the observables of the $\beta\gamma$ system on a $2$-disc).
Consider the standard description of $\PP^1 = U \cup V$ where $U = {\rm Spec}(\CC[\gamma])$ and $V = {\rm Spec}(\CC[\gamma^{-1}])$.

On $U$, $2\CDO_{\PP^1}(U)$ is the graded polynomial algebra $\CC[\gamma[k,\ell], \beta[p,q]]$. 
On the intersection $U \cup V$ we glue by the transition function
\begin{align*}
\Tilde{\gamma} [k,\ell] & \define \gamma^{-1} [k,\ell] \\
\Tilde{\beta} [p,q] & \define - \sum_{i+j+k=p} \sum_{i'+j'+k'=q} \gamma[i,i'] \gamma[j,j'] \beta[k,k'] + 2 \gamma[p+1, q] + 2 \gamma[p, q+1] .
\end{align*}
\brian{need to fix that I think}

We can gain further insight into the structure of $2\CDO_{\PP^1}$ by the following result. 
Classically, the target $\PP^1$ has an obvious geometric symmetry by the Lie algebra $\sl(2)$ which further lifts to a symmetry by the dg Lie algebra $\fa_2 \otimes \sl(2)$.

\begin{prop}
The graded vector space $H^\bu \big(\PP^1 \; , \; 2 \CDO_{\PP^1}\big)$ is a module for the graded Lie algebra $H^\bu(\sfA_2) \otimes \sl(2)$
\end{prop}

\begin{rmk}
This result is to be contrasted with the case of ordinary CDO's on $\PP^1$. 
Classically, the one-dimensional $\beta\gamma$ system of maps $\CC \to \PP^1$ has a symmetry by the current algebra $\sfA_1 \otimes \sl(2) = \sl(2)[z,z^{-1}]$. 
At the quantum level, the global sections of ordinary CDO's over $\PP^1$ is a representation for affine Kac--Moody algebra $\Hat{\sl}_2$ at the {\em critical level} \cite[Theorem 5.7]{MSV}. 
In fact, it is isomorphic to a direct sum of two copies of the vacuum representation at the critical level.
This proposition shows that the classical $\sl(2)$-valued $S^3$-currents of global sections of 2-CDO's on $\PP^1$ acquire no such central extension. 
\end{rmk}

Instead of $\PP^1$ let's consider $\PP^2$ thought of as the Grassmannian of lines in $\CC^3$. 
Since $\ch_3(\T_{\PP^2})$ is trivial
the $\beta\gamma$ system of maps $\CC^2 \to \PP^2$ exists at the quantum level and we get a sheaf of 2-CDO's that we denote $2\CDO_{\PP^2}$. \footnote{The sheaf of ordinary CDO's is {\em not defined} on $\PP^2$.}

The classical $\beta\gamma$ system has, as a symmetry algebra, the $\sl(3)$-valued $S^3$ currents $\sfA_2 \otimes \sl(3)$. 
This is {\em not} a symmetry at the quantum level, rather a {\em higher dimensional Kac--Moody algebra} acts instead.

Let $\theta \in {\rm Sym}^3(\sl(3))$ denote the invariant polynomial $(A,B,C) \mapsto {\rm tr}(ABC)$, where the trace is computed in the {\em defining} representation.
Given $\theta$ we define, as in Section \ref{sec:KM}, the $2$-dimensional Kac--Moody algebra as the $L_\infty$ algebra central extension
\[
0 \to \CC K \to \Hat{\sl(3)}_{2,\theta} \to \sfA_2 \otimes \sl(3) \to 0 .
\]

\begin{prop}
The graded vector space $H^\bu \big(\PP^2 \; , \; 2 \CDO_{\PP^2}\big)$ is a module for the $L_\infty$ algebra $\Hat{\sl(3)}_{2, \theta}$ whereby the central element $K$ acts by multiplication by some nonzero scalar. 
\end{prop}

\subsubsection{Chiralization of the B-model}

In a precise sense, one can view the higher dimensional $\beta\gamma$ system as a holomorphic refinement of a familiar algebra in topological field theory.

\begin{prop}
Let $X$ be a complex manifold with ${\rm ch}_{3}(\T_X) = 0$ and let $2\CDO_X$ be a sheaf of $2$-CDO's on $X$. 
There is an equivalence of sheaves on $X$
\[
{\rm Zhu}_{\EE_2} \big(2\CDO_X) \simeq {\rm PV}^{\bu}_X \define \bigoplus_{i\geq 0} {\rm PV}^i_X [-i] .
\]
Furthermore, the underlying $\PP_2$-structure of the left hand side agrees with the standard Gerstenhaber structure on polyvector fields.
\end{prop}

\begin{rmk}
In this sense, $2\CDO_X$ is a `chiralization' of the sheaf of polyvector fields.
It is distinct from a more standard one coming from the holomorphic twist of the two-dimensional $\cN=(2,2)$ supersymmetric $\sigma$-model.
\end{rmk}

The expert reader will identify the sheaf appearing in the statement of this proposition as local observables of the topological $B$-model on $\RR^2$ with target $X$. 
At the level of quantum field theories, the statement of this proposition is no surprise. 
The key point is that the Zhu algebra (and its $\EE_n$ generalization) is an instance of ``dimensional reduction'' from a holomorphic theory to a topological one.

On one hand, one considers the $\beta\gamma$ of maps from the two-dimensional complex manifold $\CC^\times \times \CC^\times$ with target manifold $X$:
\[
\T^*[-1] {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , X\right) \; \simeq \; {\rm Map}\left(\CC_\dbar^\times \times \CC_\dbar^\times , \T^*[1] X\right) .
\]
In this identification we have used the obvious Calabi--Yau form on $\CC^\times \times \CC^\times$. 
The dimensional reduction of this mapping space along the `doubled' radial projection $\CC^\times \times \CC^\times \to \RR \times \RR$ is precisely the AKSZ description of the ordinary $B$-model with target $X$
\[
{\rm Map}\left(\RR^2_{\rm dR} , \T^*[1] X\right)
\]
in agreement with the proposition above.

\subsubsection{Homogenous spaces}

Suppose that $N$ is a unipotent subgroup of $G$.
For $j \geq 1$ one has
\[
H^j \left( G / N \, ; \, \Omega^{n+1,cl}_{G/N} \right) \; \simeq \; H_{\rm dR}^{j+n+1} \big(G / N \big)
\]

@@

\subsubsection{The duality functor}

There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
\begin{itemize}
\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
\item The dual of the magnetic theory is equivalent to the original electric theory. In other words, the double dual of the electric theory is equivalent to itself. 
\end{itemize}
%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
Let us briefly remark how this general duality looks classically in the holomorphic context.

Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
The superpotential is $W(QQ^\dagger, \mu)$.
The dual theory is again a holomorphic QCD theory with mesons.
Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
\beqn
(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
\eeqn
The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
\beqn
\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
\eeqn
Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.

Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
The superpotential is simply
\beqn
\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
\eeqn
The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)

\subsection{Evidence for holomorphic Seiberg duality}

We now turn to examining evidence for the conjecture, which will, in turn, allow us to refine it.
The first piece of evidence involves the classical field theories:
\begin{enumerate}
\item[(1)] Each theory has a moduli space of vacua, and there is a natural isomorphism between the spaces for theories dual according to the conjecture.
\end{enumerate}
This map determines a map of factorization algebras of classical observables,
and it should deform to the map between the factorization algebras for the quantum theories.
(There are some interesting geometric subtleties --- about stacks versus their affinizations --- that we discuss below.)

As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
and these can be matched under the duality. 
For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
Under quantization, these have isomorphic anomalies.
\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out these assertions.

\subsubsection{Moduli of vacua and quantization}

It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
and we call such a solution a {\em classical vacuum}.
Thus each theory has an associated {\em moduli space of classical vacua},
which we describe below.
Each vacuum determines a perturbative field theory that one could try to quantize,
and we have shown the following.
(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)

\begin{thm}
Both $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F, \check{N})$ exist at the quantum level for any choice of classical vacuum. 
That is, the anomaly to a perturbative BV quantization vanishes.
In fact, the quantization is one-loop exact. 
\end{thm}

It is common in physics to study field theories defined on the spacetime $\RR^n$.
As the underlying spacetime $\RR^n$ is a group under addition (i.e., it is the translation group),
it is natural to ask for field theories with an action by translations.
That is, since the fields are sections of a fiber bundle over $\RR^n$,
one can ask for an equivariant fiber bundle and ask for the equations of motion (or action functional) to be equivariant under translations.
In practice, physicists often work with field theories whose equations of motion are differential equations with constant coefficients.
(Nearly all the examples we've discussed in this survey satisfy this condition.)

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong [V/G]
\]
where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong [\fg^*/G],
\]
the coadjoint quotient stack of the group.
\brian{The paragraph began with holomorphic theories, do you want to say twist of 4d N=1?}
(We are working in a $\ZZ/2$-graded world here.)
Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong [X/G]
\]
where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.

In studying questions about the classical vacua of supersymmetric field theories, however, physicists have not typically worked with the {\em stack}.
Instead, they have worked with a GIT quotient.
For instance, in the setting of a gauge theory with moduli stack of classical vacua $[V/G]$, it means they work with 
\[
V\Sslash G = \Spec(\cO(V)^G),
\]
the scheme whose ring of functions are the $G$-invariant functions on the representation~$V$.
This affine scheme is known as the {\em affinization} of the stack $V/G$, as it is the best affine approximation to the stack (i.e., apply the left adjoint to the inclusion of affine schemes among stacks).
This affinization might be seen as parametrizing ``states'' rather than solutions, 
as it is defined via functions on the solutions (see Remark~\ref{sols vs states} for more on this aspect).

We will call this GIT quotient the moduli {\em space} of classical vacua and denote it by~$M_{\rm vac}(\cT)$.
Note that the font of M changes between stack and space.

\begin{rmk}
In practice physicists work with ordinary schemes (i.e., without any derived directions), 
although one can also study the derived affine scheme that is the best approximation to a derived stack.
Below we will always provide an ordinary scheme as the moduli {\em space},
following the physicists.
\end{rmk}

It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
The canonical map
\[
[V/G] \to V\Sslash G
\]
often collapses orbits together.
An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$.
Its affinization is
\[
\gl_N \Sslash GL_N \cong \CC^N
\]
by the Chevalley restriction theorem, 
which says $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
(The rightmost algebra is symmetric polynomials in the eigenvalues.)
The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
In other words, the canonical map collapses together Jordan blocks with the same diagonal entries.
For this reason, it loses details about the classical vacua remembered by the stack quotient.

\begin{rmk}\label{sols vs states}
The physicists' focus on the moduli space is not unreasonable:
one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
and hence records much more about the classical theory; 
the space cannot distinguish between some vacua because it collapses orbits.
Moreover, the stack encodes much more data about the theory near each vacuum.
For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
\end{rmk}

For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac}(\cT_{\sfE}(F,N)) \cong T^*[1] \left(V_Q \times V_Q^*/SL(N)\right).
\]
By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
Before we describe the full space, let's examine a simpler case involving just the quarks.
A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
and it is a classic result of invariant theory that
\[
\Hom(\CC^F, \CC^N)\Sslash SL(N) \cong \widehat{{\rm Gr}(F, N)} \subset \Lambda^N \CC^F
\]
where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.

>>>>

\usepackage{macros, setspace}
\usepackage{epigraph}

@@

\dedicatory{In memory of Yuri Manin, with gratitude and admiration.}

\maketitle

\epigraph{\itshape The mathematical language of classical physics is based upon real numbers \dots The mathematical language of quantum physics is based upon complex numbers, and it would be natural to expect that the complex analytic and the algebraic geometry should replace the differential geometry of the classical period.}{Yuri Manin from the introduction of {\it Frobenius Manifolds, Quantum Cohomology, and Moduli Spaces}}

\tableofcontents

@@

A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
When $\Sigma$ is a surface this theory can be written in such a way that makes its complex structure apparent.
First, we complexify the field $\phi$ which we can view as a pair of fields $\gamma, \Bar{\gamma}$.
When we do this, we can split it up into its chiral and anti-chiral `sectors'.
By chiral (anti-chiral) we mean part involving $\gamma$ ($\Bar{\gamma}$).
The holomorphic part is described by the following action
\beqn
\int_\Sigma \beta \wedge \dbar \gamma
\eeqn
where $\beta$ is a $(1,0)$ form on $\Sigma$ and should be thought of as a Lagrange multiplier for the field $\del \Bar{\gamma}$ which we now think about as having its own degrees of freedom (this is called the first-order formalism).
There is also a coupling between the chiral and anti-chiral sectors, 
for more details we refer to \cite{Kapustin,GGW}. 
This piece of the free boson is the simplest holomorphic field theory; aptly called the $\beta\gamma$-\textit{system}.
It plays a role in superstring theory as the free field theory underlying bosonic ghosts corresponding to worldsheet supersymmetry~\cite{Polchinski}.

There is a holomorphic field theory defined on an arbitrary complex manifold as a simple generalization of this `$\beta\gamma$ system'.
The input data is simply a complex manifold $X$ of arbitrary complex dimension $n$ together with a (super) holomorphic vector bundle $V$ on~$X$.
Above we took this bundle to be trivial.
The fields of the theory consist of pairs 
\begin{align*}
\gamma & \in \Gamma(X,V)\\
\beta & \in \Omega^{n,n-1}(X,V^*) .
\end{align*}
The action functional is identical $\int_X \beta \wedge \dbar \gamma$.

Notice that when $n = \dim_\C X > 1$ that there is a linear symmetry present in the above action given by shifting $\beta$ by a $\dbar$-exact form
\beqn
\beta \mapsto \beta + \dbar \eta , \quad \eta \in \Omega^{n,n-2}(X,V^*)
\eeqn
For this model to be well-posed at the quantum level we must include the ghosts $\eta$.
Further, $\eta$ can be shifted by an exact form in a way that does not effect the above gauge transformation, so we must also include ghosts for ghosts, etc..
This is one of the key differences between the ordinary $\beta\gamma$ system and its higher dimensional version.
Nevertheless, many techniques we have for understanding free field theories can still by applied to this model as we will explain later in this note.

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
\beqn
\dbar \mu + \frac12 [\mu,\mu] = 0 ,
\eeqn
where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.

\subsection{The local definition, and examples from supersymmetric field theories}

@@

There is the following local characterization of a holomorphic field theory, 
which allows us to connect directly to supersymmetric field theories. 
Suppose that our spacetime is $\CC^n = \RR^{2n}$ and assume that the theory we are considering is translation invariant, meaning that there is an action buy the $2n$-dimensional Lie algebra spanned by the vector fields $\del / \del {z_i}, \del / \del {\zbar_i}$ for $i=1,\ldots,n$. 
In a holomorphic theory we require that the anti-holomorphic vector fields $\del / \del {\zbar_i}$ act homotopically trivial. 
In the derived world this is prescribed by the data of homotopy trivializations for such vector fields.

@@

\owen{I suggest we mostly move this to a later section and expand it substantially.}

@@

Let $V$ be a vector space.
Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
To a disc $D = D_r(z)$ this assigns the following cochain complex
\beqn
\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
\eeqn
where the differential is $\dbar + \triangle$ which we will explain momentarily. 
We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
\beqn
\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
\eeqn
The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
The vertex algebra associated to this disk algebra is the familiar $\beta\gamma$-vertex algebra.

@@

\section{Constructing examples \& renormalization}

\owen{We should review BW results and subsequent improvements by Gaiotto et al and Wang}

@@

\subsection{A remark relating to homological projective duality}
